Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-20 revision-1/lang.tex
checkpoint

To capture this distinction we introduce a function $\otp$
with the following specification:
$$
\delta(\otp,v_1,v_2) \defeq v_1 \fplus v_2
$$
Although the semantics are the same as addition, the use of $\otp$
makes a declarative distinction. But more importantly we will be
able to assign a type to $\otp$ that enforces the one-time discipline
on its first argument via type linearity, and reflects hiding of
its second argument via security type labels, as will be discussed in Section
\ref{section-types}.

@@

$$
m_\cid = k_\cid + (k_\Delta * v)
$$

$$
\delta(\macotp,v_1,v_2) \defeq v_1 \macplus v_2
$$

$$
\delta(\macauth, (v, [\ldots,m_\cid,\ldots]), k_\cid) \defeq
     (v, [\ldots,m_\cid,\ldots]) \text{\ if\ } m_\cid = k_\cid + (k_\Delta * v)
$$

$$
\begin{array}{lcl}
  \elab{\mesg{a}}{2} &:=&
  \elab{(\macotp\ \macgv{\elab{\secret{x}}{1}}\ \macgv{\elab{\flip{a}}{\Oracle}})}{1}\\
  \elab{\mesg{a}}{1} &:=&
  \elab{(\macotp\ \macgv{\elab{\secret{x}}{1}}\ \macgv{\elab{\flip{a}}{\Oracle}})}{2}\\
  \elab{\mesg{b}}{2} &:=&
  \elab{(\macotp\ \macgv{\elab{\secret{y}}{2}}\ \macgv{\elab{\flip{b}}{\Oracle}})}{1}\\
  \elab{\mesg{b}}{1} &:=&
  \elab{(\macotp\ \macgv{\elab{\secret{y}}{2}}\ \macgv{\elab{\flip{b}}{\Oracle}})}{2}\\
  \elab{\mesg{d}}{1} &:=&
  \elab{(\macauth(\mesg{a}, \mack{\macx{\secret{x}}{1}}{2} \fminus \mack{\macx{\flip{a}}{\Oracle}}{2}) \macplus (\macgv{\elab{\secret{x}}{1}}\macminus\macgv{\elab{\flip{a}}{\Oracle}}))}{1}\\
  \elab{\mesg{e}}{1}&:=&
  \elab{(\macauth(\mesg{b}, \mack{\macx{\secret{y}}{2}}{2} \fminus \mack{\macx{\flip{b}}{\Oracle}}{2}) \macplus (\macgv{\elab{\secret{y}}{2}}\macminus\macgv{\elab{\flip{b}}{\Oracle}}))}{1}\\
  \rvl{1} &:=&
  \elab{( (\mesg{d} \mactimes \mesg{e}) \macplus
          (\mesg{d} \mactimes \macgv{\elab{\flip{b}}{\Oracle}}) \macplus
          (\mesg{e} \mactimes \macgv{\elab{\flip{a}}{\Oracle}}) \macplus \macgv{\elab{\secret{c}}{\Oracle}}
    )}{1}\\
  \elab{\mesg{d}}{2} &:=&
  \elab{(\macauth(\mesg{a}, \mack{\macx{\secret{x}}{1}}{1} \fminus \mack{\macx{\flip{a}}{\Oracle}}{1}) \macplus (\macgv{\elab{\secret{x}}{1}}\macminus\macgv{\elab{\flip{a}}{\Oracle}}))}{2}\\
  \elab{\mesg{e}}{2}&:=&
  \elab{(\macauth(\mesg{b}, \mack{\macx{\secret{y}}{2}}{1} \fminus \mack{\macx{\flip{b}}{\Oracle}}{1}) \macplus (\macgv{\elab{\secret{y}}{2}}\macminus\macgv{\elab{\flip{b}}{\Oracle}}))}{2}\\
  \rvl{2} &:=&
  \elab{( (\mesg{d} \mactimes \mesg{e}) \macplus
          (\mesg{d} \mactimes \macgv{\elab{\flip{b}}{\Oracle}}) \macplus
          (\mesg{e} \mactimes \macgv{\elab{\flip{a}}{\Oracle}}) \macplus \macgv{\elab{\secret{c}}{\Oracle}}
    )}{2}\\
  \out{1} &:=& \elab{(\rvl{1} \macplus \macauth(\rvl{2},\ldots))}{1} \\
  \out{2} &:=& \elab{(\macauth(\rvl{1},\ldots) \macplus \rvl{2})}{2}
\end{array}
$$

>>>>

To capture this distinction we introduce a function $\otp$
with the following specification:
$$
\delta(\otp,v_1,v_2) \defeq \fcod{v_1 \fplus v_2}
$$
Although the semantics are the same as addition, the use of $\otp$
makes a declarative distinction. But more importantly we will be
able to assign a type to $\otp$ that enforces the one-time discipline
on its first argument via type linearity, and reflects hiding of
its second argument via security type labels, as will be discussed in Section
\ref{section-types}.

@@

A field value $v$ is secret shared among $n$ clientz in BDOZ as follows.
Each client $\cid$ in a federation of size $n$ gets a value of the form
$(v_\cid,[m_1,\ldots,m_n])$, where $v_\cid$ is a secret
share of $v$, i.e., $v = \fcod{v_1 \fplus \cdots \fplus v_n}$. Further, 
values $[m_1,\ldots,m_n]$ are MACs of $v_\cid$, such that
$m_{\cid'} = k_{\cid'} + (k_\Delta * v_\cid)$ for each $\cid'\in [1..n]$,
where keys $k_{\cid'}$ and $k_\Delta$ are known only to $\cid$
and $k_\Delta$ is common to all MACs used by $\cid$. By
extending certain field operations to these forms, denoted $\macv$,
a form of semi-homorphic encryption is obtained that is adequate to compute
Beaver Triples. For example, if keys $k_1$ and $k_2$ authenticate
$\macv_1$ and $\macv_2$, then $k_1 \fplus k_2$ authenticates
$\macv_1 \macplus \macv_2$,  where $\macplus$ is addition
extended to MACed values. Relevant semantic rules for this, as
well as multiplication of MACed and field values, are given in
Figure \ref{fig-bdoz}- for more details the reader is referred to
\cite{XXX}.

We define variable forms $\macx{\secret{w}}{\cid}$ and
$\macx{\flip{w}}{\cid}$ range over local MACed shares of a secret and
random sample owned by client $\cid$, respectively. We let
$\mack{\macx{x}{\cid_1}}{\cid_2}$ denote the key that
authenticates $\cid_n$'s share of $\cid_1$'s value $x$.
We also assume a key $\flip{\ttt{delta}}$ on each client
$\cid$, which is that client's $k_\Delta$, 
In Figure \ref{fig-bdoz} we define the relevant properties
of pre-processed stores.

Similarly to field values, we can use MACed shares in
uniform independent distributions as one-time-pads for
hiding other values, using subtraction over MACed shares.
So we introduce a function $\macotp$ to do this
declaratively.
$$
\delta(\macotp,v_1,v_2) \defeq \fcod{v_1 \macminus v_2}
$$
Also, we can define a $\macauth$ function that authenticates
a client $\cid$'s share, and an $\macopen$ function
that extracts a field value from its shares.
\begin{mathpar}
\delta(\macauth, (v, [\ldots,m_\cid,\ldots]), k_\cid) \defeq
     (v, [\ldots,m_\cid,\ldots]) \text{\ if\ } m_\cid = \fcod{k_\cid \fplus (k_\Delta \ftimes v)}

\delta(\macopen, (v_1, [\ldots]), \ldots, (v_n, [\ldots]),) \defeq
\fcod{v_1 \fplus \cdots \fplus v_n}
\end{mathpar}
This authentication eliminates cheating and guarantees protocol
integrity. As we will show in Section \ref{section-types}, this
can be reflected in a security type for $\macauth$.

Putting these pieces together, we can implement 2-party multiplication with
Beaver Triples as follows. Recall that Beaver Triples are values
$(a,b,c)$ such that $c = \fcod{b \ftimes a}$- we implement them here
as a secret $\secret{c}$ and samples $\flip{a}$ and $\flip{b}$ owned
by an \emph{oracle} $\Oracle$ that we always assume is honest but is
otherwise not involved in the protocol. We define pre-processing
properties of Beaver Triples in Figure \ref{figure-bdoz}. First,
clients 1 and 2 compute (aka \emph{open}) $\secret{x} \fplus \flip{a}$ and
$\secret{y} \fplus \flip{b}$ where
$\secret{x}$ and $\secret{y}$ are 1 and 2's secrets respectively.
Note that both perform a \emph{secure opening} by authenticating
each others' shares and record $\secret{x} \fplus \flip{a}$ and
$\secret{y} \fplus \flip{b}$ as $\mesg{d}$ and $\mesg{e}$ respectively.
$$
\begin{array}{lcl}
  \elab{\mesg{a}}{2} &:=&
  \elab{(\macotp\ \macgv{\elab{\flip{a}}{\Oracle}}\ \macgv{\elab{\secret{x}}{1}})}{1}\\
  \elab{\mesg{a}}{1} &:=&
  \elab{(\macotp\ \macgv{\elab{\flip{a}}{\Oracle}}\ \macgv{\elab{\secret{x}}{1}})}{2}\\
  \elab{\mesg{b}}{2} &:=&
  \elab{(\macotp\ \macgv{\elab{\flip{b}}{\Oracle}}\ \macgv{\elab{\secret{y}}{2}})}{1}\\
  \elab{\mesg{b}}{1} &:=&
  \elab{(\macotp\ \macgv{\elab{\flip{b}}{\Oracle}}\ \macgv{\elab{\secret{y}}{2}})}{2}\\
  \elab{\mesg{d}}{1} &:=&
  \elab{(\macopen\ \macauth(\mesg{a}, \mack{\macx{\secret{x}}{1}}{2} \fminus \mack{\macx{\flip{a}}{\Oracle}}{2}) \ (\macgv{\elab{\secret{x}}{1}}\macminus\macgv{\elab{\flip{a}}{\Oracle}}))}{1}\\
  \elab{\mesg{e}}{1}&:=&
  \elab{(\macopen\ \macauth(\mesg{b}, \mack{\macx{\secret{y}}{2}}{2} \fminus \mack{\macx{\flip{b}}{\Oracle}}{2}) \ (\macgv{\elab{\secret{y}}{2}}\macminus\macgv{\elab{\flip{b}}{\Oracle}}))}{1}\\
  \elab{\mesg{d}}{2} &:=&
  \elab{(\macopen\ \macauth(\mesg{a}, \mack{\macx{\secret{x}}{1}}{1} \fminus \mack{\macx{\flip{a}}{\Oracle}}{1}) \ (\macgv{\elab{\secret{x}}{1}}\macminus\macgv{\elab{\flip{a}}{\Oracle}}))}{2}\\
  \elab{\mesg{e}}{2}&:=&
  \elab{(\macopen\ \macauth(\mesg{b}, \mack{\macx{\secret{y}}{2}}{1} \fminus \mack{\macx{\flip{b}}{\Oracle}}{1}) \ (\macgv{\elab{\secret{y}}{2}}\macminus\macgv{\elab{\flip{b}}{\Oracle}}))}{2}
\end{array}
$$
Now, each client uses their share of $\secret{c}$ to generate their
share of the final output, which is again reported via a secure opening.
Homomorphic key calculations are elided for brevity.
$$
\begin{array}{lcl}
  \rvl{1} &:=&
  \elab{( (\mesg{d} \ftimes \mesg{e}) \macplus
          (\mesg{d} \mactimes \macgv{\elab{\flip{b}}{\Oracle}}) \macplus
          (\mesg{e} \mactimes \macgv{\elab{\flip{a}}{\Oracle}}) \macplus \macgv{\elab{\secret{c}}{\Oracle}}
    )}{1}\\
  \rvl{2} &:=&
  \elab{( (\mesg{d} \ftimes \mesg{e}) \macplus
          (\mesg{d} \mactimes \macgv{\elab{\flip{b}}{\Oracle}}) \macplus
          (\mesg{e} \mactimes \macgv{\elab{\flip{a}}{\Oracle}}) \macplus \macgv{\elab{\secret{c}}{\Oracle}}
    )}{2}\\
  \out{1} &:=& \elab{(\macopen\ \rvl{1} \ \macauth(\rvl{2},\ldots))}{1} \\
  \out{2} &:=& \elab{(\macopen\ \macauth(\rvl{1},\ldots) \ \macauth(\rvl{2},\ldots))}{2} 
\end{array}
$$
Some information about input secrets is revealed by the product, but
secure opening ensures high integrity and hence robustness to
corruption, aka robust declassification.
